\begin{abstract}

论文的摘要是对论文研究内容和成果的高度概括。摘要应对论文所研究的问题及其研究目的进行描述，对研究方法和过程进行简单介绍，对研究成果和所得结论进行概括。

摘要应具有独立性和自明性，其内容应包含与论文全文同等量的主要信息。使读者即使不阅读全文，通过摘要就能了解论文的总体内容和主要成果。

论文摘要的书写应力求精确、简明。切忌写成对论文书写内容进行提要的形式，尤其要避免“第1章……；第2章……；……”这种或类似的陈述方式。

其他要求：

（1）文字：中文和英文各一份；中、英文摘要及其关键词分别各置一页内；字号小四宋体；

（2）字数：中文600 字左右；英文3500 字符左右；

（3）字号字体：小四号宋体。

关键词是为了文献标引工作、用以表示全文主要内容信息的单词或术语，能体现论文的主要内容，词组符合学术规范。

关键词3-5个，不超过5个，每个关键词中间用分号隔开。

\end{abstract}

\keywords{关键词1；关键词2；关键词3；关键词4；关键词5}

\begin{enabstract}

An abstract of a dissertation is a summary and extraction of research work and contributions. Included in an abstract should be description of research topic and research objective, brief introduction to methodology and research process, and summarization of conclusion and contributions of the research. An abstract should be characterized by independence and clarity and carry identical information with the dissertation. It should be such that the general idea and major contributions of the dissertation are conveyed without reading the dissertation. 

An abstract should be concise and to the point. It is a misunderstanding to make an abstract an outline of the dissertation and words “the first chapter”, “the second chapter” and the like should be avoided in the abstract. 

Other requirements:

(1) Text: one copy in Chinese and one copy in English; the Chinese and English abstracts and their key words are placed on one page respectively; the font size is small four Song typeface;

(2) Number of words: about 600 in Chinese and 3500 in English;

(3) Font size: Times New Roman, small four.

Keywords are terms used in a dissertation for indexing, reflecting core information of the dissertation. It can reflect the main content of the paper, and the phrases conform to the academic norms.

An abstract may contain 3-5 key words, no more than 5,with semi-colons used in between to separate one another.


\end{enabstract}

\enkeywords{keyword 1; keyword 2; keyword 3; keyword 4; keyword 5}
